Multi-modality Imagery Database for Plant Phenotyping

### 2015-04-28 datapaper_prior.tex

>>>>

One of our data modalities is dense depth measurement.  This has been a component of a number of recent non-plant RGB-D databases designed for object recognition~\cite{Lai2011}, scene segmentation~\cite{Silberman2011}, human analysis~\cite{Sung2011,Barbosa:reid12}, and mapping~\cite{sturm12iros}.  By including dense depth for a plant database we anticipate enabling development of new 3D plant shape analysis algorithms.
